Exploratory data analysis

### 2021-11-02 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

```{r buffer-scenarios-1, echo=FALSE}
knitr::include_graphics("inst/tree-buffer-vis.png")
```

@@

```{r buffer-scenarios-2, echo=FALSE}
knitr::include_graphics("inst/tree-buffer-vis-max.png")
```

>>>>

```{r buffer-scenarios-1, echo=FALSE}
knitr::include_graphics("docs/figure/tree-buffer-vis.png")
```

@@

```{r buffer-scenarios-2, echo=FALSE}
knitr::include_graphics("docs/figure/tree-buffer-vis-max.png")
```
